Exploring Rural Shrink Smart Through Guided Discovery Dashboards

### 2022-07-31 SDSS Journal Paper/Paper Draft.Rmd
A few structural changes to the second version

\db{In the initial design, we included a map for each vital service, this initially created a lag for the users' experience. As a result, we cached map directions from OSRM for each service in our database, which drastically changed the response time for the user. Our initial design lack proper dashboard design, which would allow the user's eye to focus on the most important parts of the dashboard. The redesign allowed for a cleaner box from the top to the bottom. }

\db{In addition to the timing due to the map loading slowly, we added the vital statistics at the county level to allow for a more robust understanding of the town and it's surroundings. The rurality index allowed for a better classification index, the USDA source also allowed for the town to understand how much or little the closest major city is impacting their towns. Town members are commuting into the next town for work or resources, this could be helpful to know which services and resources to add into their own town.}

\db{In regards to the Parallel Coordinate Plots, we wanted to declutter the aspects of the x- and y-axis that will allow for a less overwhelming experience for our users. Our x-axis had a large number of variables that our team precevied to be the best variables. This sparked the need to make sure that only necessary variables are placed in the graph, along with the way they were placed along the x-axis. We decided to limit the variables to those open source variables that were related directly to QoL. The variables were then placed in a bulks based on QoL topic.}

>>>>

\db{In the initial design, we included a map for each vital service, this initially created a lag for the users' experience. As a result, we cached map directions from OSRM for each service in our database, which drastically} \svp{reduced} \db{the response time for the user. Our initial design \svp{did not naturally focus} the user's eye on the most important parts of the dashboard; the redesign allowed for a cleaner \svp{flow} from the top to the bottom. }

\db{In addition to the timing due to the map loading slowly, we added the vital statistics at the county level to allow for a more robust understanding of the town and it's surroundings. The rurality index \svp{provided a better classification} and the USDA sources allowed for the town to understand \svp{the impact of} the closest major city \svp{due to commuting for work and shopping at larger stores not available within the town}.}

\svp{We also modified the parallel coordinate plots in several ways:}

- Our x-axis had a large number of variables that we as researchers believed to be the most strongly associated with quality of life. However, there were still too many variables for users to successfully parse. We reduced the number of variables, focusing on variables that had the highest data quality, and we grouped these variables by quality of life factor [@petersCommunityResiliencyDeclining2019]. 
- Originally, parallel coordinate bands were scaled based on the selected comparison towns. This had the effect of truncating the range of variables and over-emphasizing differences between selected towns relative to the overall range of each variable over all towns in our data set. We chose to show all towns in the data set in a very light $\alpha$ grey color to provide some information about the overall range of each variable. Unfortunately, even with the low-$\alpha$ value, this increased the visual complexity of the plot and confused users. Future iterations will likely make use of another aesthetic, such as boxplots or violin plots, to show the range of values for all towns, and then use lines only for towns that are selected by the user. This should strike a balance between visual complexity and representing the data accurately.
- We noticed that users did not make use of our suggested comparison towns, and so we removed that option in favor of allowing users to enter their own comparison towns directly. Users already had pre-determined towns they wanted to compare to, and our suggestions were just in the way.

<!-- \db{In regards to the Parallel Coordinate Plots, we wanted to declutter the aspects of the x- and y-axis that will allow for a less overwhelming experience for our users. Our x-axis had a large number of variables that our team precevied to be the best variables. This sparked the need to make sure that only necessary variables are placed in the graph, along with the way they were placed along the x-axis. We decided to limit the variables to those open source variables that were related directly to QoL. The variables were then placed in a bulks based on QoL topic.} -->

\svp{While not all of these modifications were well received in our second round of user testing, the changes did incrementally move the dashboard display towards our goal of allowing users to explore the data and engage with it. We continued to be surprised with how well users reacted to the parallel coordinate plots, which we initially thought might be too abstract for users unfamiliar with multivariate data displays, but the ability to compare towns across multiple dimensions and examine the similarities and differences between their approaches to different services seemed to be intuitive for users once they understood that each vertical axis was a different variable.}

### 2022-07-31 SDSS Journal Paper/Paper-Draft.tex
A few structural changes to the second version

{\textcolor{blue}{In the initial design, we included a map for each vital service, this initially created a lag for the users' experience. As a result, we cached map directions from OSRM for each service in our database, which drastically changed the response time for the user. Our initial design lack proper dashboard design, which would allow the user's eye to focus on the most important parts of the dashboard. The redesign allowed for a cleaner box from the top to the bottom. }}

{\textcolor{blue}{In addition to the timing due to the map loading slowly, we added the vital statistics at the county level to allow for a more robust understanding of the town and it's surroundings. The rurality index allowed for a better classification index, the USDA source also allowed for the town to understand how much or little the closest major city is impacting their towns. Town members are commuting into the next town for work or resources, this could be helpful to know which services and resources to add into their own town.}}

{\textcolor{blue}{In regards to the Parallel Coordinate Plots, we wanted to declutter the aspects of the x- and y-axis that will allow for a less overwhelming experience for our users. Our x-axis had a large number of variables that our team precevied to be the best variables. This sparked the need to make sure that only necessary variables are placed in the graph, along with the way they were placed along the x-axis. We decided to limit the variables to those open source variables that were related directly to QoL. The variables were then placed in a bulks based on QoL topic.}}

>>>>

{\textcolor{blue}{In the initial design, we included a map for each vital service, this initially created a lag for the users' experience. As a result, we cached map directions from OSRM for each service in our database, which drastically}} {\textcolor{red}{reduced}} {\textcolor{blue}{the response time for the user. Our initial design {\textcolor{red}{did not naturally focus}} the user's eye on the most important parts of the dashboard; the redesign allowed for a cleaner {\textcolor{red}{flow}} from the top to the bottom. }}

{\textcolor{blue}{In addition to the timing due to the map loading slowly, we added the vital statistics at the county level to allow for a more robust understanding of the town and it's surroundings. The rurality index {\textcolor{red}{provided a better classification}} and the USDA sources allowed for the town to understand {\textcolor{red}{the impact of}} the closest major city {\textcolor{red}{due to commuting for work and shopping at larger stores not available within the town}}.}}

{\textcolor{red}{We also modified the parallel coordinate plots in several ways:}}

\begin{itemize}
\tightlist
\item
  Our x-axis had a large number of variables that we as researchers believed to be the most strongly associated with quality of life. However, there were still too many variables for users to successfully parse. We reduced the number of variables, focusing on variables that had the highest data quality, and we grouped these variables by quality of life factor \citep{petersCommunityResiliencyDeclining2019}.
\item
  Originally, parallel coordinate bands were scaled based on the selected comparison towns. This had the effect of truncating the range of variables and over-emphasizing differences between selected towns relative to the overall range of each variable over all towns in our data set. We chose to show all towns in the data set in a very light \(\alpha\) grey color to provide some information about the overall range of each variable. Unfortunately, even with the low-\(\alpha\) value, this increased the visual complexity of the plot and confused users. Future iterations will likely make use of another aesthetic, such as boxplots or violin plots, to show the range of values for all towns, and then use lines only for towns that are selected by the user. This should strike a balance between visual complexity and representing the data accurately.
\item
  We noticed that users did not make use of our suggested comparison towns, and so we removed that option in favor of allowing users to enter their own comparison towns directly. Users already had pre-determined towns they wanted to compare to, and our suggestions were just in the way.
\end{itemize}

{\textcolor{red}{While not all of these modifications were well received in our second round of user testing, the changes did incrementally move the dashboard display towards our goal of allowing users to explore the data and engage with it. We continued to be surprised with how well users reacted to the parallel coordinate plots, which we initially thought might be too abstract for users unfamiliar with multivariate data displays, but the ability to compare towns across multiple dimensions and examine the similarities and differences between their approaches to different services seemed to be intuitive for users once they understood that each vertical axis was a different variable.}}
